% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}    

%first of all, my thanks goes out to 
First of all, I would like to express my utmost gratitude to my supervisors, Manda Banerji and Paul Hewett, for their help and endless patience through the years. Their kindness, even through setbacks and the many delays, means a lot to me. I also want to thank Bob Carswell for his kind assistance with proofreading updates of my work and helping to keep me on track, and Adam Muzzin for useful discussions about photometry. And I am much indebted to Debbie for her outstanding administrative support. \par

%like to express my gratitude to
I would also like to extend my sincere thanks to my parents, without whose generous support finishing this thesis would not have been possible. On top of that, the kindness and moral support from my grandmothers and other family has also been immensely valuable to me. 

%I am also grateful for all the kindness and moral support from my lovely grandmothers. \par



Then, a big thanks goes out to all my friends. To my butler, my master, my butler's dog, and our hippie hermit friend, for the many crazy and incredible adventures we've had throughout the years. To Danny, Ben, and Jo, for introducing me to me a world more amazing than I could ever have imagined. To RockSoc for the fun and silliness that kept me sane. To Serena for being there with me along the way. To my Rum Party friends who, even though we are no longer regularly together often, are still so close to my heart that I could not omit their importance to my life, and therefore to this work. And to Oscar, whose unrelenting support and personal example helped me to learn to write up this large project by myself. \par

And finally, this thesis would not have come together without the people who, throughout my life, inspired in me a love for science, and I am grateful to every single one of them. %would like to thank?



\end{acknowledgements}
